Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-10-03 arxiv/examples.tex
finish section 3 with examples

We begin by considering a setting where the feature covariates are the same across all tasks but their labels are different.
In the random-effects model, we assume that every $\beta_i$ is equal to a shared component $\beta_0$ plus a task-specific component.
Suppose that the entries of $\beta_0$ are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
Suppose further that $\beta_i$ is equal to $\beta_0$ plus a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
Thus, for any two $\beta_i$ and $\beta_j$, their distance is roughly $d^2$.
Using our results, we show that the prediction loss of the hard parameter sharing estimator is as follows.

>>>>

We begin by considering a setting where the feature covariates are the same across all tasks but their labels are different.

Using our results, we show that the prediction loss of the hard parameter sharing estimator is as follows.

### 2020-10-03 arxiv/setup.tex
finish section 3 with examples

%\noindent\textbf{Positive/Negative transfer.}

\subsection{Hard Parameter Sharing}

@@

>>>>

@@

\subsection{Hard Parameter Sharing}\label{sec_hps}

\paragraph{Random-effects model.}
A natural special case of the linear model is when every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
Let $\beta_0$ denote the shared component whose entries are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
Let the task-specific component be a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
Thus, for any two different $\beta_i$ and $\beta_j$, their distance is roughly $d^2$.
%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
